Policy optimization for dynamic spatiotemporal systems \hspace{1em} \insertframenumber

### 2014-09-19 pot/LaTeX/skewnormal.tex
Manuscript updates

\subsection{Hierarchical model}\label{s:hier}
Conditioned on $z_{tk}(\bs) \iid $ $N(0, \sigma^2_{tk})$, $\sigma^2_{tk}(\bs) \sim IG(a, b)$, and $P_tk$, the marginal distributions are skew-$t$ and the joint distribution within a partition is multivariate skew-$t$.
However, we do not fix the partitions, they are treated as unknown and updated in the MCMC.
We model this with a Bayesian hierarchical model as follows.
Let $w_{t1}, \ldots, w_{tK}$ be a set of daily spatial knots in a spatial domain of interest, $\calD$, so that
\begin{align*}
 P_{tk} = \{\bs : k = \argmin_\ell || \bs_t - w_{t\ell} ||\}.
\end{align*}
Then
\begin{align}
   Y_t(\bs) \mid \Theta, z_{t}(\bs) &= X_t(\bs) \beta + \alpha z_t(\bs) + \sigma
   _t(\bs) v_t(\bs) \label{eq:hier}\\
   z_t(\bs) &= z_{tk} \text{ if } \bs \in P_{tk}\\
   \sigma^2_{t}(\bs) &= \sigma^2_{tk} \text{ if } \bs \in P_{tk}\\
   z_{tk} \mid \sigma^2_{tk} &\sim N_{(0, \infty)}(0, \sigma^2_{tk})\\
   \sigma^2_{tk} &\iid IG(\alpha, \beta)\\
   v_t(\bs) \mid \Theta &\sim \Matern(0, \Sigma)\\
   \alpha &\sim N(0, 10)\\
   w_{tk} &\sim Unif(\calD)
\end{align}
where $\Theta = \{w_{t1}, \ldots, w_{tK}, \beta, \sigma_t, \alpha, \lambda, \rho, \nu \}$; \mbox{$k = \argmin_\ell ||\bs - \bw_\ell ||$}; and $\Sigma$ is a \Matern covariance matrix with variance one, spatial range $\rho$, smoothness $\nu$.

>>>>

\subsection{Hierarchical model}\label{s:hier}
Conditioned on $z_{tk}(\bs) \iid $ $N(0, \sigma^2_{tk})$, $\sigma^2_{tk}(\bs) \sim IG(a, b)$, and $P_{tk}$, the marginal distributions are skew-$t$ and the joint distribution within a partition is multivariate skew-$t$.
However, we do not fix the partitions, they are treated as unknown and updated in the MCMC.
We model this with a Bayesian hierarchical model as follows.
Let $w_{t1}, \ldots, w_{tK}$ be a set of daily spatial knots in a spatial domain of interest, $\calD$, so that
\begin{align*}
 P_{tk} = \{\bs : k = \argmin_\ell || \bs_t - w_{t\ell} ||\}.
\end{align*}
Then
\begin{align}
   Y_t(\bs) \mid z_{t}(\bs), \sigma^2(\bs), P_{tk}, \alpha, \beta, \Theta &= X_t(\bs) \beta + \alpha z_t(\bs) + \sigma_t(\bs) v_t(\bs) \label{eq:hier}\\
   z_t(\bs) &= z_{tk} \text{ if } \bs \in P_{tk}\\
   \sigma^2_{t}(\bs) &= \sigma^2_{tk} \text{ if } \bs \in P_{tk}\\
   \alpha &\sim N(0, 10)\\
   v_t(\bs) \mid \Theta &\sim \Matern(0, \Sigma)\\
   z_{tk} \mid \sigma^2_{tk} &\sim N_{(0, \infty)}(0, \sigma^2_{tk})\\
   \sigma^2_{tk} &\iid IG(\alpha, \beta)\\   
   w_{tk} &\sim Unif(\calD)
\end{align}
where $\Theta = \{\rho, \nu, \gamma\}$; \mbox{$k = \argmin_\ell ||\bs - \bw_\ell ||$}; and $\Sigma$ is a \Matern covariance matrix with variance one, spatial range $\rho$, smoothness $\nu$, and the proportion of variance accounted for by the spatial variation is $\gamma$.
